Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-05 doc/prelim/presentation/prelim_presentation.tex
updated storage slide
reduced nonlinear preliminaries to 1 slide

  \begin{itemize}
  \item We interpret the exact solution $\ve{u}$ to be the roots of
    $\ve{F}(\ve{u})$
  \item Taylor expand the residuals at the $k+1$ iterate about the $k$
    iterate
  \end{itemize}

@@

  \begin{itemize}
  \item Assert $\ve{u}^{k+1}$ is the exact solution
  \end{itemize}

  \[
  -\ve{F}(\ve{u}^{k}) = \ve{F}'(\ve{u}^{k})(\ve{u}^{k+1}-\ve{u}^{k})
  \]

  \begin{itemize}
  \item $\ve{F}'(\ve{u}^{k})$ is the \textit{Jacobian}
    $\ve{J}(\ve{u})$
  \end{itemize}

  \[
  J_{ij} = \frac{\partial F_i(\ve{u})}{\partial u_j}
  \]

  \begin{itemize}
  \item $(\ve{u}^{k+1}-\ve{u}^{k})$ is the solution update from the
    $k$ iterate to the $k+1$ iterate
  \end{itemize}

  \[
  \delta \ve{u}^k = \ve{u}^{k+1}-\ve{u}^{k}
  \]

@@

  \pause 
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {If we need 25 Krylov iterations to converge...}
    \begin{itemize}
    \item Break even scenario: $4q+1 = m$
    \item Jacobian and probability matrix with 6 bands or less is
      cheaper
    \end{itemize}
  \end{beamerboxesrounded}

>>>>

  \begin{itemize}
  \item We interpret the exact solution $\ve{u}$ to be the roots of
    $\ve{F}(\ve{u})$
  \end{itemize}

@@

@@

  \pause 
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {If we need 25 Krylov iterations to converge...}
    \begin{itemize}
    \item Break-even scenario: $4q+1 = m$
    \item Jacobian and probability matrix storage with 6 bands or less
      is cheaper
    \end{itemize}
  \end{beamerboxesrounded}
